MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-03-25 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
archived versions of ensembl down, using current versions

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", 
                host = "uswest.ensembl.org", 
                dataset = "hsapiens_gene_ensembl")

>>>>

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", 
                host = "uswest.ensembl.org", # Ensembl Release 99 (January 2020)
                dataset = "hsapiens_gene_ensembl")
